---
title: 'NxtIRF: 1 - Generating a Reference'
author: "Alex Chit Hei Wong"
date: "`r Sys.Date()`"
output:
    rmarkdown::html_vignette:
        toc: true
vignette: >
    %\VignetteIndexEntry{NxtIRF: 1 - Generating a Reference}
    %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---

NxtIRF needs to generate a set of reference files in order to 
perform downstream applications including running the IRFinder
algorithm, collating these output files into an experiment, and
drawing visualisation tools. This vignette will show how to
generate a reference using either the command-line interface, or
the graphics user interface (GUI).

# Command Line Interface

## Setting up the Reference directory

First, load the NxtIRF package and navigate to your desired project path:

```{r, eval = FALSE}
library(NxtIRF)
setwd("/path/to/project") # Replace this with the path to your project
```

Next, create (or assign) a directory to contain the NxtIRF reference

```{r, eval = FALSE}
if(!dir.exists("Reference")) dir.create("Reference")
reference_path = "./Reference"
```

## Setting up the Reference directory
